Usage metrics

### 2021-03-04 analysis/usage.Rmd
Improve

```{r read, message=TRUE, include=F}
read_fst(corpus_path) %>% as_tibble() -> C_raw
read_csv(static_path) %>% semi_join(C_raw, by = "package") -> P

@@

```{r exercised-vs-static, include=FALSE}
# stat_evl <- P %>% filter(call_fun_name == "eval")        %>% nrow()
stat_evq <- P %>% filter(call_fun_name == "evalq")       %>% nrow()
stat_evp <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
stat_loc <- P %>% filter(call_fun_name == "local")       %>% nrow()

>>>>

```{r read, message=TRUE, include=F}
read_fst(corpus_path) %>% as_tibble() -> C_raw

# We do the semi join to only keep the file that are loadable
read_csv(static_path) %>% semi_join(C_raw, by = "package") -> P

@@

```{r exercised-vs-static, include=FALSE}
 stat_evl <- P %>% filter(call_fun_name == "eval")        %>% nrow()
stat_evq <- P %>% filter(call_fun_name == "evalq")       %>% nrow()
stat_evp <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
stat_loc <- P %>% filter(call_fun_name == "local")       %>% nrow()
